Cost-Benefit Analysis

### 2023-05-30 workflow/notebooks/cost-benefit-analysis.Rmd
Plot decision curves

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

```{r decision-curve}
library(here)
library(tidyverse)
thresh_dat <- read_csv(here('results','thresholds_results_aggregated.csv'))
thresh_dat %>% 
  filter(dataset == 'int',outcome=='attrib',seed==100) %>% 
  ggplot(aes(decision_threshold, net_benefit, 
             color = strategy, linetype = strategy)) +
  geom_line(alpha = 0.6) +
  theme_sovacool()
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE,
                      fig.path = 'figures/')
```

@@

```{r decision-curve}
library(here)
library(schtools)
library(tidyverse)
thresh_dat <- read_csv(here('results','thresholds_results_aggregated.csv'))

max_thresholds <- thresh_dat %>% 
  filter(strategy == 'model') %>% 
  group_by(dataset, outcome, strategy, decision_threshold)  %>% 
  summarize(mean_nb = mean(net_benefit)) %>% 
  filter(mean_nb < 0) %>% 
  slice_min(mean_nb) %>% 
  ungroup() %>% 
  mutate(max_thresh = decision_threshold) %>% 
  select(dataset,outcome,max_thresh)

thresh_dat %>% 
  left_join(max_thresholds, by = join_by(dataset, outcome)) %>% 
  filter(decision_threshold <= max_thresh) %>% 
  group_by(dataset, outcome, strategy, decision_threshold) %>% 
  summarize(mean_nb = mean(net_benefit)) %>% 
  ggplot(aes(decision_threshold, mean_nb, 
             color = strategy, linetype = strategy)) +
  geom_line(alpha = 0.6) +
  facet_grid(dataset ~ outcome, scales = 'free') +
  theme_sovacool()
```
